Channel Shaping Using Beyond Diagonal RIS: Analysis, Optimization, and Enhanced Flexibility

### 2025-02-11 poster/beamer.tex
:lipstick: Update poster
:construction: Updating results

		\begin{column}{\colwidth}
			\begin{block}{Overview}
				\begin{itemize}\setlength\itemsep{20pt}
					\item \textbf{What does this paper investigate?}

@@

				Assume the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible (i.e., $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$).
				For one channel realization, we can reveal channel singular values achieved by \gls{d}- and \gls{bd}-\gls{ris} by grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$.
				\begin{figure}
					\centering
					\includegraphics[width=0.41\columnwidth]{../assets/simulation/singular_trend.eps}
					% \caption{
					% 	\setlength{\leftskip}{\leftmargini}
					% 	\setlength{\rightskip}{\leftmargini}
					% 	Singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris}.
					% 	The maximum and minimum singular values are marked explicitly on the plot.}
				\end{figure}
				Here, both singular values are manipulated up to $\pm 9\%$ by \gls{d}-\gls{ris} and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris}, using 2 and 3 circuit components respectively.
			\end{exampleblock}
		\end{column}

@@

		\begin{column}{\colwidth}
			\vspace{-0.5cm}
			\begin{prop}{\gls{dof}}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				In point-to-point \glsfmtshort{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than \gls{d}-\gls{ris}.
			\end{prop}

@@

		\begin{column}{\colwidth}
			\vspace{-0.5cm}
			\begin{algo}{Group-wise geodesic optimization for \gls{bd}-\gls{ris}}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				% A geodesic is a curve representing the shortest path between two points in a Riemannian manifold.
				For \gls{bd}-\gls{ris} optimization problem of the form
				\begin{maxi*}
					{\scriptstyle{\mathbf{\Theta}}}{f(\mathbf{\Theta})}{}{}
					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{}
				\end{maxi*}
				% At iteration $r$, the $g$-th group is updated by \textcolor{imperialblue}{geodesic} \gls{rcg}
				we propose a \textcolor{pink!50!pink!75!black}{geodesic} \gls{rcg} algorithm below.
				\vspace{0.5cm}

>>>>

		\begin{column}{\colwidth}
			\vspace{-0.5cm}
			\begin{block}{Overview}
				\begin{itemize}\setlength\itemsep{20pt}
					\item \textbf{What does this paper investigate?}

@@

				Assume the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible (i.e., $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$).
				For one channel realization, we can reveal channel singular values achieved by \gls{d}- and \gls{bd}-\gls{ris} by grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$.
				\begin{figure}
					\centering
					\includegraphics[width=0.41\columnwidth]{../assets/simulation/pc_singular_trend.eps}
					% \caption{
					% 	\setlength{\leftskip}{\leftmargini}
					% 	\setlength{\rightskip}{\leftmargini}
					% 	Singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris}.
					% 	The maximum and minimum singular values are marked explicitly on the plot.}
				\end{figure}
				Here, both singular values are manipulated up to $\pm 9\%$ by \gls{d}-\gls{ris} and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris}, using 2 and 3 circuit components respectively.
			\end{exampleblock}
		\end{column}

@@

		\begin{column}{\colwidth}
			\vspace{-1cm}
			\begin{prop}{\gls{dof}}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				In point-to-point \glsfmtshort{mimo}, \gls{bd}-\gls{ris} may achieve a larger or smaller \gls{dof} than \gls{d}-\gls{ris}.
			\end{prop}

@@

		\begin{column}{\colwidth}
			\vspace{-1cm}
			\begin{algo}{Group-wise geodesic optimization for \gls{bd}-\gls{ris}}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				% A geodesic is a curve representing the shortest path between two points in a Riemannian manifold.
				For \gls{bd}-\gls{ris} optimization problem of the form
				\begin{maxi*}
					{\scriptstyle{\mathbf{\Theta}}}{f(\mathbf{\Theta})}{}{}
					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{}
				\end{maxi*}
				% At iteration $r$, the $g$-th group is updated by \textcolor{imperialblue}{geodesic} \gls{rcg}
				we propose a \textcolor{pink!50!pink!75!black}{geodesic} \gls{rcg} algorithm below.
				\vspace{0.5cm}
